---
title: "Atmutscreen_plate11"
author: "Liz Hughes"
date: "2023/05/17"
output: 
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# At Plate reader assay 11 : Check phenotype of dblGAT201 At mutants in RPMI at 37 degrees

 At dbl-GAT201 mutant P2.7ZH_G4-G12, H1-H11 from Plate 1_P2,7ZH(glycerol stock, called dblGAT201a)  in RPMI at 37 degrees.
1 Bioreps, 3 Techreps each.
Grow 5ml culture from colony (1 colony = 1 Biorep) in YPD, 30C, 180 rpm ON.
Seed at OD 600nm = 0.2 , 200 ul per well.
Run for 136 cycles.

```{r load_packages_2}

library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(rmarkdown)
library(cowplot)
library(yaml)
library(knitr)
```



# Read in transposed data as csv file RPMI

```{r csv_file_2}

rawdata <- read.csv("../Input/20230517_Atmutant_Screen_plate11_csv.csv")

```

# Change time in seconds to time in days RPMI

```{r mutate_time_2}

 rawdata_day<-mutate(rawdata, Time = Time/86400)

```

# Tidy the data using the melt function from reshape2 RPMI

```{r reshape_2}

reshaped <- melt(rawdata_day, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file RPMI

```{r Load_platemap_2}

platemap <- read.csv("../Input/20230517_RPMI_Atmut_screen_Plate11_setup.csv") %>%     
  dplyr::mutate(
    Strain = factor(Strain, 
                    levels = c( "P2.7G4","P2.7G5","P2.7G6","P2.7G7","P2.7G8","P2.7G9","P2.7G10","P2.7G11","P2.7G12","P2.7H1","P2.7H2","P2.7H3","P2.7H4","P2.7H5","P2.7H6","P2.7H7","P2.7H8","P2.7H9","P2.7H10","P2.7H11"),
                    labels = c("dblGAT201a-G4", "dblGAT201a-G5", "dblGAT201a-G6", "dblGAT201a-G7", "dblGAT201a-G8", "dblGAT201a-G9", "dblGAT201a-G10", "dblGAT201a-G11", "dblGAT201a-G12", "dblGAT201a-H1", "dblGAT201a-H2", "dblGAT201a-H3", "dblGAT201a-H4", "dblGAT201a-H5", "dblGAT201a-H6", "dblGAT201a-H7", "dblGAT201a-H8", "dblGAT201a-H9", "dblGAT201a-H10", "dblGAT201a-H11"))
  )
head(platemap, n=10)


```

# Combine the reshaped data with the plate map, pairing them by Well 

```{r join_2}

annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation? RPMI

```{r plot_blank_ODs_2}

ggplot(data=filter(annotated,is.na(Strain)),
          aes(x=Time, y=OD595,  group = Well)) + 
          geom_line() + 
          labs(x="Time (days)", y="Absorbance at 595 nm")
```


```{r plot_individual_blank_wells_2}

ggplot(data=filter(annotated,Well=="F1"), 
       aes(x=Time, y=OD595, group = Well)) + 
 
       geom_line() + 
     theme_bw()+
     labs(x="Time (hrs)", y="Absorbance at 595 nm")

```


Remove well A7, F1

## Calculate median OD for blank wells for each growth medium RPMI


```{r calc_blank_medians_2}

blank_OD_summary <- annotated %>%
   filter(is.na(Strain), Time < 1/24) %>%
  filter(Well != "A7") %>%
  filter(Well != "F1") %>%
  group_by(Media) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs) RPMI

```{r subtract_blank_OD_2}

normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Media") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all RPMI

```{r plot_all_2}

ggplot(data=normalisedOD %>%
                       filter( !is.na(Strain) ), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.15),expand=c(0,0))+
       facet_wrap(Strain ~ .)+
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()
```


## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary_At2}

ggplot(data=normalisedOD  %>%
          #dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)", "GAT201", "P2.7A1","P2.7A2","P2.7A3","P2.7A4","P2.7A5","P2.7A6","P2.7A7","P2.7A8","P2.7A9","P2.28A1","P2.28A2","P2.28A3","P2.28A4","P2.28A5","P2.28A6","P2.28A7","P2.28A8","P2.28A9" )))%>%
                     filter( !is.na(Strain) ),  
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
        stat_summary(fun = "median", geom = "line", size = 0.5) +
       scale_y_continuous(limits=c(0,0.12),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "At mutant screen", subtitle = "Plate 11: RPMI at 37 degrees") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
    guides(color=guide_legend(ncol=2))+
 theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )
       
```


```{r save_RMPI_PR2_At_Allsum.png}

ggsave("../Results/AllSummary_At11.png",width = 8,height=5)
```


## Plot OD all stat_summary(geom -"line") Highlight summary line RPMI

```{r plot_all_stat_summary_At2}


ggplot(data=normalisedOD  %>%
          #dplyr::mutate(Strain = factor(Strain, levels = c("KN99 (WT)", "GAT201", "P2.7A1","P2.7A2","P2.7A3","P2.7A4","P2.7A5","P2.7A6","P2.7A7","P2.7A8","P2.7A9","P2.28A1","P2.28A2","P2.28A3","P2.28A4","P2.28A5","P2.28A6","P2.28A7","P2.28A8","P2.28A9" )))%>%
                     filter( !is.na(Strain) ),  
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 0.5) +
       scale_y_continuous(limits=c(0,0.12),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
   
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "GAT201 Targets", subtitle = "Plate 11: RPMI at 37 degrees") +

                  theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
             theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
            guides(color=guide_legend(ncol=2))+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
      theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
            panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 1))+
      theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
```

```{r save_RMPI_PR2_At2_statsum.png}

ggsave("../Results/Statsumm_At11.png",width = 8,height=5)
```




