---
title: "Atmutscreen_plate4"
author: "Liz Hughes"
date: "2023/04/07"
output: output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# At Plate reader assay 4 : Check phenotype of dblGAT201 At mutants in RPMI at 37 degrees

Test At dbl-GAT201 mutant P2.7ZH_B7-B12 and C1-C4 from Plate 1_P2.7ZH(glycerol stock) and At dbl-GAT201 mutant P2.28EH_B7-B12 and C1-C4 from Plate 1_P2.28EH(glycerol stock) in RPMI at 37 degrees.
There is no WT KN99 alpha or Gat201 deletion on this plate.
1 Bioreps, 3 Techreps each.
Grow 5ml culture from colony (1 colony = 1 Biorep) in YPD, 30C, 180 rpm ON.
Seed at OD 600nm = 0.2 , 200 ul per well.
Run for 147 cycles.

```{r load_packages_4}

library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(rmarkdown)
library(cowplot)
library(yaml)
library(knitr)
```



# Read in transposed data as csv file RPMI

```{r csv_file_4}

rawdata <- read.csv("../Input/20230407_RPMI_Atmut_screen_Plate4_csv.csv")

```

# Change time in seconds to time in days RPMI

```{r mutate_time_4}

 rawdata_day<-mutate(rawdata, Time = Time/86400)

```

# Tidy the data using the melt function from reshape2 RPMI

```{r reshape_4}

reshaped <- melt(rawdata_day, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file RPMI

```{r Load_platemap_4}

platemap <- read.csv("../Input/20230407_RPMI_Atmut_screen_Plate4_setup.csv")
head(platemap, n=50)


```

# Combine the reshaped data with the plate map, pairing them by Well 

```{r join_4}

annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation? RPMI

```{r plot_blank_ODs_4}

ggplot(data=filter(annotated,Strain==""),
           aes(x=Time, y=OD595, color=Strain, group = Well)) + 
       geom_line() + 
       facet_grid(Media ~ .) +
       labs(x="Time (days)", y="Absorbance at 595 nm")
```


```{r plot_individual_blank_wells_4}

ggplot(data=filter(annotated,Well=="G12"), 
       aes(x=Time, y=OD595, color=Strain, group = Well)) + 
 
       geom_line() + 
     theme_bw()+
     labs(x="Time (hrs)", y="Absorbance at 595 nm")

```

Remove well A6, A12, H3, F1.

## Calculate median OD for blank wells for each growth medium RPMI


```{r calc_blank_medians_4}

blank_OD_summary <- annotated %>%
  filter(Strain=="") %>%
  filter(Well != "A6") %>%
  filter(Well != "A12") %>%
  filter(Well != "H3") %>%
  filter(Well != "F1") %>%
    group_by(Media) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs) RPMI

```{r subtract_blank_OD_4}

normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Media") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all RPMI

```{r plot_all_4}

ggplot(data=normalisedOD %>%
                      filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
       scale_y_continuous(limits=c(0,0.025),expand=c(0,0))+
       facet_wrap(Strain ~ .)+
  
       labs(x = "Time(Hrs)",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()
```




## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary_At4}

ggplot(data=normalisedOD %>%
          dplyr::mutate(Strain = factor(Strain, levels = c("P2.7B7","P2.7B8","P2.7B9","P2.7B10","P2.7B11","P2.7B12","P2.7C1","P2.7C2","P2.7C3","P2.7C4","P2.28B7","P2.28B8","P2.28B9","P2.28B10","P2.28B11","P2.28B12","P2.28C1","P2.28C2","P2.28C3","P2.28C4" )))%>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       stat_summary(fun = "median", geom = "line", size = 0.5) +
       scale_y_continuous(limits=c(0,0.05),expand=c(0,0), breaks = c(0, 0.25, 0.05)) +
  
       labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "At mutant screen", subtitle = "Plate 4: RPMI at 37 degrees") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
    guides(color=guide_legend(ncol=2))+
 theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )

ggplot
       
```


```{r save_RMPI_PR4_At_Allsum.png}

ggsave("../Results/AllSummary_At4.png",width = 8,height=5)
```


## Plot OD all stat_summary(geom -"line") Highlight summary line RPMI

```{r plot_all_stat_summary_At4}

ggplot(data=normalisedOD %>%
          dplyr::mutate(Strain = factor(Strain, levels = c("P2.7B7","P2.7B8","P2.7B9","P2.7B10","P2.7B11","P2.7B12","P2.7C1","P2.7C2","P2.7C3","P2.7C4","P2.28B7","P2.28B8","P2.28B9","P2.28B10","P2.28B11","P2.28B12","P2.28C1","P2.28C2","P2.28C3","P2.28C4" )))%>%
                     filter(Strain != ""), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 0.5) +
       scale_y_continuous(limits=c(0,0.05),expand=c(0,0), breaks = c(0, 0.25, 0.05)) +
    labs(x = "Number of Days",
            y = "Absorbance (595nm)",
            title = "At mutant screen", subtitle = "Plate 3: RPMI at 37 degrees") +
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
    guides(color=guide_legend(ncol=2))+
 theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )
```

```{r save_RMPI_PR4_At4_statsum.png}

ggsave("../Results/Statsumm_At4.png",width = 8,height=5)
```








