---
title: "Atmutscreen_plate5"
author: "Liz Hughes"
date: "2023/05/01"
output: 
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# At Plate reader assay 5 : Check phenotype of dblGAT201 At mutants in RPMI at 37 degrees

Test At dbl-GAT201 mutant P2.7ZH_C5-C12 and D1-D12 and E1 from Plate 1_P2,7ZH(glycerol stock, called dblGAT201a) in RPMI at 37 degrees.
1 Bioreps, 3 Techreps each.
Grow 5ml culture from colony (1 colony = 1 Biorep) in YPD, 30C, 180 rpm ON.
Seed at OD 600nm = 0.2 , 200 ul per well.
Run for 143 cycles.

```{r load_packages_5}

library("reshape2")
library(dplyr)
library(ggplot2)
library(tidyverse)
library(rmarkdown)
library(cowplot)
library(yaml)
library(knitr)
```



# Read in transposed data as csv file RPMI

```{r csv_file_5}

rawdata <- read.csv("../Input/20230427_RPMI_Atmut_screen_Plate5_csv.csv")

```

# Change time in seconds to time in days RPMI

```{r mutate_time_5}

 rawdata_hour<-mutate(rawdata, Time = Time/3600)

```

# Tidy the data using the melt function from reshape2 RPMI

```{r reshape_5}

reshaped <- melt(rawdata_hour, id=c("Time", "Temp"), 
                              variable.name="Well",
                              value.name="OD595")

summary(reshaped)
```

# Read in the Plate map data from csv file RPMI

```{r Load_platemap_5}

platemap <- read.csv("../Input/20230427_RPMI_Atmut_screen_Plate5_setup.csv") %>%     
  dplyr::mutate(
    Strain = factor(Strain, 
                    levels = c("P2.7C5", "P2.7C6","P2.7C7","P2.7C8","P2.7C9","P2.7C10","P2.7C11","P2.7C12","P2.7D1","P2.7D2", "P2.7D3","P2.7D4","P2.7D5","P2.7D6","P2.7D7","P2.7D8","P2.7D9","P2.7D10","P2.7D11","P2.7D12","P2.7E1"),
                    labels = c("dblGAT201a-C5", "dblGAT201a-C6","dblGAT201a-C7","dblGAT201a-C8","dblGAT201a-C9","dblGAT201a-C10","dblGAT201a-C11","dblGAT201a-C12","dblGAT201a-D1","dblGAT201a-D2", "dblGAT201a-D3","dblGAT201a-D4","dblGAT201a-D5","dblGAT201a-D6","dblGAT201a-D7","dblGAT201a-D8","dblGAT201a-D9","dblGAT201a-D10","dblGAT201a-D11","dblGAT201a-D12","dblGAT201a-E1"))
  )
head(platemap, n=10)


```

# Combine the reshaped data with the plate map, pairing them by Well 

```{r join_5}

annotated <- inner_join(reshaped, platemap, by="Well")
 
```

# How stable are ODs of blank wells, to use for normalisation? RPMI

```{r plot_blank_ODs_5}

ggplot(data=filter(annotated,is.na(Strain)),
           aes(x=Time, y=OD595,  group = Well)) + 
           geom_line() + 
           labs(x="Hours", y="Absorbance at 595 nm")
```


```{r plot_individual_blank_wells_5}

ggplot(data=filter(annotated,Well=="G12"), 
       aes(x=Time, y=OD595, group = Well)) + 
 
       geom_line() + 
     theme_bw()+
     labs(x="Hours", y="Absorbance at 595 nm")

```

Remove well A1,A6,D1,F1,H6,H7,G12

## Calculate median OD for blank wells for each growth medium RPMI


```{r calc_blank_medians_5}

blank_OD_summary <- annotated %>%
  filter(is.na(Strain), Time < 1/24) %>%
  filter(Well != "A6") %>%
  filter(Well != "A1") %>%
    group_by(Media) %>%
  summarise(OD_median=median(OD595),
            OD_mean=mean(OD595),
            OD_max=max(OD595),
            OD_min=min(OD595))
print(blank_OD_summary)
```

# Subtract blank OD to make corrected OD and Plot OD_corrected v Time (hrs) RPMI

```{r subtract_blank_OD_5}

normalisedOD <- annotated %>%
  left_join(blank_OD_summary, by="Media") %>%
  mutate(OD_corrected = OD595 - OD_median)

```

## Plot OD all RPMI

```{r plot_all_At5}

ggplot(data=normalisedOD %>%
                      filter( !is.na(Strain) ), 
                      aes(x=Time, y=OD_corrected, color=Strain, group = Well)) + 
       geom_line() + 
  scale_x_continuous(limits = c(0,24)) +
       scale_y_continuous(limits=c(0,0.12),expand=c(0,0))+
       facet_wrap(Strain ~ .)+
  
       labs(x = "Hours",
            y = "Absorbance (595nm)") +
       theme(text = element_text(size = 20))+
       theme_bw()
```

## Plot OD all stat_summary(geom -"line") remove excess lines RPMI

```{r plot_stat_summary_At5}

ggplot(data=normalisedOD  %>%
         
                     filter( !is.na(Strain) ), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       
       stat_summary(fun = "median", geom = "line", size = 0.5) +
  scale_x_continuous(limits = c(0,24)) +
       scale_y_continuous(limits=c(0,0.1),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Hours",
            y = "Absorbance (595nm)",
            title = "At mutant screen", subtitle = "Plate 5: RPMI at 37 degrees") +
           
       theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
       
       theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
      guides(color=guide_legend(ncol=2))+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
  theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
         panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 2))+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5) )
       
```


```{r save_RMPI_PR5_At_Allsum.png}

ggsave("../Results/AllSummary_At5.png",width = 8,height=5)
```


## Plot OD all stat_summary(geom -"line") Highlight summary line RPMI

```{r plot_all_stat_summary_At5}

ggplot(data=normalisedOD  %>%
         
                     filter( !is.na(Strain) ), 
                      aes(x=Time, y=OD_corrected, color=Strain)) + 
       geom_line(aes(group = Well), size = 0.2, alpha = 0.2) + 
       stat_summary(fun = "median", geom = "line", size = 0.5) +
  scale_x_continuous(limits = c(0,24)) +
       scale_y_continuous(limits=c(0,0.12),expand=c(0,0), breaks = c(0, 0.05, 0.1)) +
  
       labs(x = "Hours",
            y = "Absorbance (595nm)",
            title = "At mutant screen", subtitle = "Plate 5: RPMI at 37 degrees") +
                  theme_bw() +
       theme(text = element_text(size = 15))+
       theme(axis.title = element_text(size = 15))+
             theme(axis.ticks.length = unit(0.3, "cm"))+
       theme(title = element_text(size = 15))+
       theme(panel.grid.minor = element_blank())+
            guides(color=guide_legend(ncol=2))+
       theme(legend.title = element_text(size = 15))+
      theme(legend.background = element_rect(fill = "transparent", color=NA))+
      theme(legend.key = element_rect(fill = "transparent", color=NA))+
       theme (plot.background =  element_rect(fill = "transparent", color=NA), 
            panel.background = element_rect(fill = "transparent", color=NA),)+
      theme(panel.border = element_rect(linetype = "solid", colour = "black", size = 1))+
      theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))

ggplot
```

```{r save_RMPI_PR5_At5_statsum.png}

ggsave("../Results/Statsumm_At5.png",width = 8,height=5)
```








